### 2022-04-11 src/text/3-applications-subsections/3D-analysis.tex
add Lars, mention flux points

\subsection{3D Analysis}
\label{ssec:3d-analysis}
\todo{Laura}
The 1D analysis approach is a powerful tool to measure the spectrum of an isolated source. However, more complicated situations, such as field of views containing several overlapping sources, require a more careful treatment. Because it is based on integration over a region, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region. Similarly, sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region.

\cite{Mohrmann2019}

@@

@@

%
%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering
%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
%\end{figure*}

>>>>

\subsection{3D Analysis}
\label{ssec:3d-analysis}
\todo{Laura}
The 1D analysis approach is a powerful tool to measure the spectrum of an isolated source. However, more complicated situations require a more careful treatment. In fields of view containing several overlapping sources, the 1D approach can't disentangle the contribution of each source to the total flux in the selected region. Sources with extended or complex morphology can result in the measured flux being underestimated, and heavily dependent on the choice of extraction region. Additionally, the 1D approach neglects the energy-dependence of the PSF.

@@

A thorough description of the 3D analysis approach and multiple examples that use \gammapy can be found in~\cite{Mohrmann2019}. Here we present a short example to highlight some of its advantages.

@@

Note that all the models fitted also have a spectral component, from which flux points can be derived in a similar way as described in~\ref{ssec:1d-analysis}.
%
%\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
%Ref:~\citep{Stewart2009} \begin{figure*}[t] \centering
%	\includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
%	\caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
%\end{figure*}
